meeting q

### 2020-11-05 meetingquestions.Rmd
removed journalist killed and everything but oecd and latin america

```{r}
dep_vars <- select(data, ends_with("_fh")) %>% names()
resp_vars <- select(data, -ends_with("_fh")) %>% names()
dep_vars
resp_vars
```

@@

```{r}
p1 <- data %>% 
  ggplot(mapping = aes(x = -freedix_fh)) + 
  geom_histogram(bins = 15) + labs(title = "Freedom Index", subtitle = 'Further Right More "Free"')

p2 <- data %>% 
  ggplot(mapping = aes(x = -polrights_fh)) + 
  geom_histogram(bins = 15) + labs(title = "Political Rights Index")

p3 <- data %>% 
  ggplot(mapping = aes(x = -cliberities_fh)) + 
  geom_histogram(bins = 15) + labs(title = "Civil Liberties Index")

p1 + p2 + p3

@@

Missing values

@@

Best subsets resuls show most vars are insignificant. Can we procede with the project?

@@

subsets %>% 
  ggplot(aes(x = df, y = adj.r.squared)) + 
  geom_point() + 
  geom_smooth(data = r, aes(df, adj), se = FALSE, span = 0.5, color = "Green") + 
  labs(title = "Best Subsets", x = "Parameters", y = "Adjusted R Squared")
```
at 5 degrees of freedom
```{r}
model_df5 <- subsets %>% filter(df == 5) %>% 
  arrange(desc(adj.r.squared)) %>% 
  select(model) %>% head(1) %>% as.character()

model_df5
fit <- lm(model_df5, data = data)
summary(fit)
```

>>>>

```{r}
dep_vars <- select(data, ends_with("_fh")) %>% names()
resp_vars <- select(data, -ends_with("_fh")) %>% names()
# note all.equal(data$cliberities_fh, data$freedix_fh)
dep_vars
resp_vars
```

@@

```{r}

p1 <- data %>% 
  ggplot(mapping = aes(x = -polrights_fh)) + 
  geom_histogram(bins = 15) + labs(title = "Political Rights Index", subtitle = 'Further Right More "Free"')

p2 <- data %>% 
  ggplot(mapping = aes(x = -cliberities_fh)) + 
  geom_histogram(bins = 15) + labs(title = "Civil Liberties Index", subtitle = 'Further Right More Civli Liberties')

p1 + p2

@@

Missing values we are running into a lot of incomplete rows. If we drop all the NA we lose more than 90% of our data.

@@

Best subsets results show most vars are insignificant. Can we proceed with the project?

@@

subsets %>% 
  ggplot(aes(x = df, y = adj.r.squared)) + 
  geom_point() + 
  geom_smooth(data = r, aes(df, adj), se = FALSE, span = 0.5, color = "Green") + 
  labs(title = "Best Subsets", x = "Parameters", y = "Adjusted R Squared")
```

at 5 degrees of freedom
```{r}
model_df5 <- subsets %>% filter(df == 5) %>% 
  arrange(desc(adj.r.squared)) %>% 
  select(model) %>% head(1) %>% as.character()

model_df5
fit <- lm(model_df5, data = data)
summary(fit)
